Plant trait cleaning and combining

### 2024-05-22 code/L1/L1_LastStep_DiversityInputObjects.Rmd
add function to creat presence-absence-matrix by resolution -- this has not been tested yet

@@

>>>>

```{r}
# Define the function
create_presence_absence_matrix <- function(resolution_meters, species_sf) {
  # Make the grid
  TAGrid <- TApoly %>%
    st_make_grid(cellsize = c(resolution_meters)) %>%
    st_intersection(TropicalAndes_IUCNHabitat_Forest) %>%
    st_cast("MULTIPOLYGON") %>%
    st_sf() %>%
    mutate(cellid = row_number())

  # Join species data to the grid
  species_grid <- TAGrid %>%
    st_join(species_sf) %>%
    filter(!is.na(species)) %>%
    select(cellid, species)

  # Create the presence-absence matrix
  presence_absence_matrix <- species_grid %>%
    mutate(presence = 1) %>%
    pivot_wider(names_from = species, values_from = presence, values_fill = list(presence = 0)) %>%
    as.data.frame()

  # Ensure the cellid column is the first column
  presence_absence_matrix <- presence_absence_matrix %>%
    select(cellid, everything())

  return(presence_absence_matrix)
}
```

```{r}
presence_absence_matrix <- create_presence_absence_matrix(resolution_meters, species_sf)
```

@@

```{r}
summary(plant_PAM_matrix)
summary(frugivore_PAM_matrix)
```
